---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

## Question 1

```{r}
library(classdata)
head(ames)
tail(ames)
library(ggplot2)

```

- Parcel id: character, Unique ID for each house, N/A
- address: character, address of each house, N/A
- style: character, what style type each house is, 1 story - 3 story
- occupancy: character, how the house is occupied, N/A
- sale date: numerical, date the house was sold, 1-1-2020 - 12-31-2022
- sale price: numerical, the price the house was sold at, 0-700,000
- muti-sale: character, wheather or not there was mutiple sales, N/A
- year built: numerical, year the house was built, 1920-2022
- acres: Numerical, how many acres the property has, 0-2 acres
- total living area:Numerical,the square footage of the inside of the home, 600-5000 sq ft 
- bedrooms: numerical, how many bedrooms are in the home, 0-6 bedrooms
- finished basement area:Numerical, the square footage if the home has a finished basement, 600-200 sq ft
- lot area: Numerical, size of the property in square footage, 2000-10000 sq ft
- A/C: Character, if the home has AC, yes or no
- fireplace: Character, if the home has a fireplace, yes or no
- neighborhood: Character, what neighborhood the home is in, different neighborhoods in Ames

## Question 2 

We found the variable of interest to be Sale Price

## Question 3 



```{r}
library(ggplot2)
ggplot(ames, aes(x=Bedrooms))+
  geom_bar(aes(weight = `Sale Price`))+ 
  ggtitle("Sale Price Compared to Bedrooms")

# Minimum Sale Price
min(ames$`Sale Price`, na.rm = TRUE)

# Maximum Sale Price
max(ames$`Sale Price`, na.rm = TRUE)
```
#### The minimum for the value of Sale Price is 0 and the maximum is 20,500,000. The general pattern between the Sale Price and the number of bedrooms is as the number of bedrooms increase so does the Sale Price. There is an odd part of the data that starts at five bedrooms or more, it does not seem to follow this pattern as the Sale Price seems to go down.



## Question 4 

### Allison's work: 

```{r}
ggplot(data = ames, aes(x = `LotArea(sf)`, y = `Sale Price`)) +
  geom_point()

```

The values for the Lot area don't seem to change the sale price by too much, but it does seem that as lot area square footage increases, so does sale price. There are a few oddities with very high sale prices and one with a very high lot area. There are also some rows missing values. 

### Kelly's work:
```{r}
ggplot(ames, aes(x=`LotArea(sf)`, y=`Sale Price`))+
  geom_point(alpha=0.6, color="purple")+ labs( title = "Relationship between Sale Price and Lot Area", x="Lot Area", y="Sale Price") +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  coord_cartesian(xlim = c(0, 45000), ylim = c(0, 1500000)) +
  theme_minimal()


# Minimum LotArea(sf)
min(ames$`LotArea(sf)`, na.rm = TRUE)

# Maximum LotArea(sf)
max(ames$`LotArea(sf)`, na.rm = TRUE)
```
#### The range of the chosen variable, lot area, is 0-523228. The scatterplot shows that as Lot Area increases, Sales Price decreases. This seems to be counter intuitive but there are a lot of factors that impact Sales Price as location. Large lots in rural area are less than large areas in urban areas. This kind of follows the pattern in the previous graph after 5 bedrooms.

### Kenzie's work: 

### Marcus's work: 

